\documentclass[18pt]{letter}
\usepackage{fullpage}
\usepackage{palatino}
\usepackage[ampersand]{easylist}
\begin{document}
{\Large \textbf{CS 261:Mathematical Foundations of Computer Science Summer 2017}}\\\\
{\large
\textbf{Instructor:} Antonio Espinoza\\\\
\textbf{email:} amajest@cs.unm.edu\\
Feel free to email me directly, I'm happy to answer questions.\\\\
\textbf{Office and Office Hours:}My office is at the Center for
Advanced Research Computing (CARC) in 1000C (its a cubicle on the
first floor). I'll hold office hours after class(12:15 -1:15) on
Monday in the STAMM room of this building (CENT), and from 2-3 on
Thursdays in my office. If these times do not work for you email me
to schedule a different meeting time.\\\\
\textbf{Course Description:}Introduction to the formal mathematical
concepts of computer science. Topics include proofs, first-order
logic, set theory, functional relations, graphs, cryptography, state
machines, and combinatorics.\\\\
\textbf{Textbook:}Discrete Mathematics and Its Applications 7th ed, by Kenneth H. Rosen

\textbf{Grading:}
For letter grade purposes: 
A+ is 100-98, A is 97-91, A- is 90-89, B+ is 88-87, B is 86-81, B- is 80-79, C+ is 78-77, C is 76-71, C- is 70-69, D is 68-60, below 60 is an F.   

\begin{easylist}[itemize]
        & 45\% Homework
        & 25\% Midterm
        & 30\% Final
\end{easylist}
\textbf{Homework:}Homework will be due at the start of class.I will
not accept late work. You can expect to be assigned one homework a
week, due on the following Tuesday.It is a good idea to start homework early in order to utilize office hours.

\textbf{Schedule:}\\\\
\begin{tabular}{l|l|l}
Week & Chapter(s) & Topics \\\hline
1  & 1         & The Foundations: Logic and Proofs       \\
2  & 2         & Basic Structures: Sets, Functions, Sequences, Sums, and Matrices       \\
3  & 3,4       & Algorithms, Number Theory and Cryptography  \\
4  & 5         & Induction and Recursion       \\
5  & 6         & Counting      \\
6  & 10        & Graphs         \\
7  & 13        & Modeling Computation       \\
8  &           & Review/Catch up
\end{tabular}

\textbf{Prerequisites:} A minimum grade of C- in Computer
Programming Fundamentals (CS151 or CS155 or CS152) and Calculus I
(MATH162).

\textbf{Absences:} This is a short 8 week course and we will be
covering a lot of material. It is important to show up every day to
class in order to not get behind. Only excused absences are allowed.

\textbf{UNM statement of compliance with ADA:}
“Qualified students with disabilities needing appropriate
academic adjustments should contact the professor as soon as possible to ensure your needs are met in
a timely manner.  Students must inform the professor of the disability early in the class so appropriate
accommodations can be met.  Handouts are available in alternative accessible formats upon request.”\\\\
\textbf{Statement about Title IX borrowed from Patrick Bridges:}
“
No form of discrimination, sexual 
harassment, or sexual misconduct will be tolerated in this class or at UNM in general. I strongly 
encourage you to report any problems you have in this regard to the appropriate person at UNM.  As 
described below, I must report any such incidents of which I become aware to the university.  UNM 
also has confidential counselors available through UNM Student Health and Counseling (SHAC), 
UNM Counseling and Referral Services (CARS), and UNM LoboRespect. UNM faculty, Teaching 
Assistants, and Graduate Assistants are considered “responsible employees” by the Department of 
Education (see pg 15 at 
http://www2.ed.gov/about/offices/list/ocr/docs/qa-201404-title-ix.pdf
).
This designation requires that any report of gender discrimination which includes sexual harassment, 
sexual misconduct, and sexual violence made to a faculty member, TA, or GA must be reported to the 
Title IX Coordinator at the Office of Equal Opportunity (oeo.unm.edu).
More information on the UNM policy regarding sexual misconduct, including reporting, counseling, 
and legal options, is available online:
https://policy.unm.edu/university-policies/2000/2740.html
”
}
\end{document}
